\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-15 report/paper.tex
wrote about future work

% Use ghost-SPH or similar

% Parallelize

>>>>

    % Use ghost-SPH or similar
    To increase the accuracy of the interaction with the boundary and free surfaces a method like ghost-SPH that was presented by Schechter et al.~\cite{ghost} could be implemented.
    A method that Bender et al.~\cite{bender} used was the versatile rigid fluid coupling method for incompressible SPH presented by Akinci et al.~\cite{akinci2012versatile}.
    It is based on static boundary particles which could also be a valid implementation to get better boundary interactions.

    % Parallelize 
    To get the simulation to be able to handle more particles the solution could be parallelized to speed up the calculations.
    This could be done using OpenMP and increasing the threading.

    % Viscosity
    To get the simulation more interesting viscosity can be introduced into the fluid simulation.
    It would make simulations of thicker fluids possible.
